---
title: "ChartkickR"
author: "Bilikisu Olatunji"
date: "2023-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Let try using the chartkickR htmwidgets sample data to create a simple charts as shown below


## Example 1 - Scatter Chart
```{r}
library(tidyverse)
library(chartkickR)
line_tbl <- read_rds("sample_data/line_data.rds")

chartkickR(data = line_tbl, x = dates,
           y = values, type = "LineChart",curve = TRUE)
           
```

## ## Example 2 - Discrete Line Chart 

```{r}
discrete_line_tbl <- read_rds("sample_data/discrete_line_data.rds")

chartkickR(data = discrete_line_tbl, x = V1,
           y = V2, type = "LineChart")
```



## Example 3 - Discrete Line Chart Numeric String

``` {r}
discrete_line_ns_tbl <- read_rds("sample_data/discrete_line_numString_data.rds")

chartkickR(data = discrete_line_ns_tbl, x = V1,
           y = V2, curve = TRUE, legend = FALSE, type = "LineChart")

```

## Example 4 - Pie Chart

``` {r}

pie_data <- read_rds("sample_data/pie_data.rds")

chartkickR::chartkickR(data = pie_data,
                       type = "PieChart",
                       colors = list("#4f86f7","#fc5a8d","yellow","red","#6f2da8"))

```


## Example 5 - Donut Chart

``` {r}
donut_data <- read_rds("sample_data/donut_data.rds")


chartkickR::chartkickR(data = donut_data, x = V1, y = V2,
                       type = "PieChart", donut = TRUE,
                       colors = list("#4f86f7", "#fc5a8d","yellow","red","#6f2da8"))

```


## Example 6 - Column Chart

``` {r}
column_data <- read_rds("sample_data/column_data.rds")


chartkickR::chartkickR(data = column_data, x = V1, y = V2,
                       type = "ColumnChart",legend = FALSE,
                       colors = list("purple", "red", "green"))

```


## Example 8 - Bar Chart

``` {r}

bar_data <- read_rds("sample_data/bar_data.rds")

chartkickR::chartkickR(data = bar_data, x = V1, y = V2,type = "BarChart", legend = FALSE, colors = list("green","red"))

```


## Example 8 - Area Chart

``` {r}
area_data <- read_rds("sample_data/area_data.rds")

chartkickR::chartkickR(data = area_data, x = Date, y = Value,
                       legend = FALSE,type = "AreaChart",curve = TRUE)
                     
```


## Example 9 - Discrete Area Chart

``` {r}

discrete_area_data <- read_rds("sample_data/discrete_area_data.rds")

chartkickR::chartkickR(data = discrete_area_data, x = country, y = values,
                       legend = FALSE,type = "AreaChart",curve = TRUE)
```


## Example 10 - Scatter Chart

``` {r}
scatter_data <- read_rds("sample_data/scatter_data.rds")

chartkickR::chartkickR(data = scatter_data, x = V1, y = V2,
                       legend = FALSE, type = "ScatterChart",colors = list("red"))

```

## Example 11 - Bubble chart ------------------

```{r}
bubble_data <- read_rds("sample_data/bubble_data.rds")


chartkickR::chartkickR(data = bubble_data, x = V1, y = V2,group = V3,
                       legend = FALSE, type = "BubbleChart",colors = list("red"))

```

## Example 12 - Large bubble chart

```{r}

bubble_lg_data <- read_csv("inst/examples/sample_data/bubble_large.csv")
write_csv(bubble_lg_data,"inst/examples/sample_data/bubble_large.csv")

chartkickR::chartkickR(data = bubble_lg_data,
                       legend = FALSE, type = "BubbleChart",colors = list("green"))

```

## Example 13 - Geo Chart

```{r}

geo_data <- read_csv("inst/examples/sample_data/geo.csv")

chartkickR::chartkickR(data = geo_data, type = "GeoChart")


```

## Example 14 - Timeline - Google Charts

```{r}
timeline_data <- read_csv("inst/examples/sample_data/timeline.csv")


chartkickR::chartkickR(data = timeline_data, type = "Timeline", colors = list("red", "green"))

```

## References:
- [Examples, Installation and Data formats](https://github.com/ankane/chartkickR.js)





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
